\textbf{ANALYSIS OF REINFORCED \\NEURAL NETWORKS}

### 2022-08-26 doc/paper.tex
removed packages that github can't render
weird stuff
fixed stupid stuff
changes
added parameters

% packages 
\usepackage[cmintegrals,cmbraces]{newtxmath}
\usepackage{ebgaramond-maths}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{amsmath}

@@

% author and supervisors
\author{\textbf{\huge-----------------------------}\\[0.5in] \textit{Adam Amanbaev, Hugo Åkerfeldt, Jonathan Hallström, Romeo Patzer} \\\\
    \small \textit{Supervisors: Ulf Backlund \& Bertil Lundberg}
}

@@

% specify font of abstract-title
\renewcommand\abstractname{\textbf{Abstract \\[0.2in] \huge---------}}

@@

% abstract page
\begin{abstract}
    In late 2017 DeepMind announced a groundbreaking system in a preprint \cite{alphazero} and the results were astonishing. The system was called AlphaZero and utilized \emph{artificial neural networks} in order to teach itself the game chess without any proprietary knowledge, except the rules. After approximately 9 hours it was able to beat the strongest hand-crafted engines, such as Stockfish and it had learned centuries of human knowledge of chess. In this paper we aim to study the effectiveness of different \emph{neural networks} such as the one used in AlphaZero. To be precise, we will analyze the efficiency of those networks in combination with varying \emph{algorithms, optimizations, hyperparameters} and \emph {architectures} applied to the classic game and variations of connect-four. \\[0.5in]
\centerline{\keywords{Machine Learning, AI, Reinforcement Learning, Neural Network, Deep Learning}} 
\end{abstract}

@@

% create sections 
\section{Introduction}

% subsection under nearest section above
\subsection{subsection}

>>>>

% packages
\usepackage[cmintegrals,cmbraces]{newtxmath}
\usepackage{ebgaramond-maths}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

@@

% author and supervisors
\author{\rule{8cm}{0.3mm} \\[0.5in] \textit{Adam Amanbaev, Hugo Åkerfeldt, Jonathan Hallström, Romeo Patzer} \\\\
    \small \textit{Supervisors: Ulf Backlund \& Bertil Lundberg}
}

@@

% specify font of abstract-title
\renewcommand\abstractname{\textbf{Abstract \\[0.13in] \rule{3cm}{0.2mm}}}

% change size of contents-title
\renewcommand\contentsname{\Huge Contents \\[5mm]}

@@

% abstract page
\begin{abstract}
    In late 2017 DeepMind announced a groundbreaking system in a preprint \cite{alphazero} and the results were astonishing. The system was called AlphaZero and utilized \emph{artificial neural networks} in order to teach itself the game chess without any proprietary knowledge, except the rules. After approximately 9 hours it was able to beat the strongest hand-crafted engines, such as Stockfish and it had learned centuries of human knowledge of chess. In this paper we aim to study the effectiveness of different \emph{neural networks} such as the one used in AlphaZero. To be precise, we will analyze the efficiency of those networks in combination with varying \emph{algorithms, optimizations, parameters, hyperparameters} and \emph {architectures} applied to the classic game and variations of connect-four. \\[0.5in]
\centerline{\keywords{Machine Learning, AI, Reinforcement Learning, Neural Network, Deep Learning}}
\end{abstract}

@@

% Motivation section before actual content
\section{Motivation}

\newpage

\section{Introduction}

\subsection{What is Reinforcement Learning}
\subsection{What is Deep Learning}
\subsubsection{Artificial Neural Networks}
\subsubsection{Deep Reinforcement Learning}

\newpage

\section{Notation and Definitions}
\subsection{Notation}

\newpage
